\backmatter

\clearpage % or \cleardoublepage
\addcontentsline{toc}{chapter}{References}

%new command added to change Bibliography title to References
\renewcommand{\bibname}{References}

\begin{thebibliography}{11}

\bibitem[Aumasson, 2017]{Aumasson}
  Aumasson J.,
  \emph{Serious cryptography: A practical introduction to modern encryption},
  No Starch Press Inc, 
  San Francisco, California, U.S.A,
  2017
  
\bibitem [Bieling, 2020]{Bieling}
  Bieling, J.,
  \emph{"Thundernest/sample-extensions: Example extensions for Thunderbird webextensions apis."},
  GitHub.,
  Document Search and Retrieval Page,
  Retrieved August 29, 2022, 
  from https://github.com/thundernest/sample-extensions 
  
\bibitem[Crawford, 2019]{Crawford}
  Crawford D.,
  \emph{“AES Encryption: Everything You Need to Know about AES.”},
   ProPrivacy.com,
   Published 4 Feb. 2019,
   Document Search and Retrieval Page,
   Retrieved August 29, 2022,
   from https://proprivacy.com/guides/aes-encryption
   
\bibitem[Delfs and Knebl, 2007]{DelfsKnebl}
  Delfs H. and H. Knebl,
  \emph{Introduction to Cryptography: Principles and Applications},
  Springer Verlag, 
  Berlin, Germany,
  2007
  
\bibitem[Dooley, 2008]{Dooley}
  Dooley, J. F.,
  \emph{History of cryptography and cryptanalysis: Codes, ciphers, and their algorithms},
   Springer International Publishing AG,
   Cham, Switzerland,
   2008
    
\bibitem[Katz \& Lindell, 2008]{Katz}
  Katz J., \& Lindell Y.,
  \emph{Introduction to modern cryptography: Principles and protocols},
  Chapman \& Hall/CRC Press,
  Boca Raton, London, New York,
  2008
    
\bibitem[Martin, 2017]{book10}
  Martin K.,
  \emph{Everyday cryptography: Fundamental principles and applications},
  Oxford University Press,
  2017
  
\bibitem[Mozilla, 2022]{WebEx}
  Thunderbird Add-on Team.,
  \emph{“Introduction to Add-on Development.”},
  Thunderbird, Mozilla, 
  Document Search and Retrieval Page,
  Retrieved August 29, 2022,
  https://developer.thunderbird.net/add-ons/mailextensions.
  
\bibitem[Nirula, 2022]{Nirula}
  Nirula U.,
  \emph{"Block Cipher | Purpose, Applications \& Examples"},
  Document Search and Retrieval Page,
  Retrieved August 29, 2022,
  https://study.com/learn/lesson/block-cipher-purpose-applications.html
   
\bibitem[Paar \& Pelzl, 2009]{PaarPelzl}
  Paar, C., \& Pelzl, J.,
 \emph{Understanding cryptography: A textbook for students and practitioners.},
  Springer Science \& Business Media,
  2009
  
\bibitem [Paar, 2014]{PaarYoutube}
  Paar, C.,
  \emph{“Lecture 7: Introduction to Galois Fields for the AES by Christof Paar.”},
  YouTube,
  Published 30 Jan. 2014, 
  Document Search and Retrieval Page,
  Retrieved August 29, 2022,
  https://www.youtube.com/watch?v=x1v2tX4\_dkQ.
  
    
\bibitem[Schneier, 2015]{Schneier}
  Schneier B.,
  \emph{Applied Cryptography: Protocols, Algorithms, and Source Code in C},
  Wiley, Indianapolis, Indiana, U.S.A,
  2015.

\bibitem[Shirey, 2007]{Shirey}
  Shirey, R.,
  \emph{“RFC 4949 - Internet Security Glossary, Version 2.”},
  Document Search and Retrieval Page,
  Aug. 2007,
  Retrieved August 29, 2022, 
  https://datatracker.ietf.org/doc/html/rfc4949. 


\bibitem[Stanford Security Lab, 2009]{SJCL}
  Stanford Security Lab,
  \emph {“Stanford Javascript Crypto Library (SJCL).”},
   SJCL: a Javascript Crypto Library, 
   Stanford University, California, U.S.A.,
   Document Search and Retrieval Page,
   Retrieved August 29, 2022,
   https://crypto.stanford.edu/sjcl/.

\end{thebibliography}